Response to the defense feedback

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Channel Capacity}
$K$ is a random variable.
Let $k$ be one of the possible
values of $K$. The Shannon entropy $H(K)$ is defined as
\begin{equation}\label{chapter5:eq1}
  H(K) = - \sum_{k {\in} K}p(k)\log_2(k)
\end{equation}

@@

\begin{mydef}
  \label{chapter5:def}
    Suppose we have a program $\beta$ with the input space $K$ and observation set $O$. We randomly select $k_1, k_2, \ldots, k_n \in K$ as the input and get observations $o_1, o_2, \ldots, o_n \in O$. Assume $K'=\{k_1, k_2, \ldots, k_n\}$  ($K' \subseteq K$) and
    $O'=\{o_1, o_2, \ldots, o_n\}$  ($O' \subseteq O$).
    We denote it as
    $$\beta(K') \rightarrow	O'.$$
    %Here $O$ is a set that consists of various observations $o_1, o_2, \dots, o_m$.
    The amount of leaked information $L_{\beta(K')\rightarrow O'}$ based on the observations ($O'$) is
    $$L_{\beta(K')\rightarrow O'} = H(O'). $$
\end{mydef}

@@

Suppose one program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
Depending on the relation between A and B, the total leaked information $L_{\mathit{total}}$ will be:

\subsection{Independent Leakages}
If A and B are independent leakages, the total information leakage will be:
\[L_{\mathit{total}} = L_A + L_B \]

\subsection{Dependent Leakages}
If A and B are dependent leakages, the total information leakage will be:
\[\max{\{L_A, L_B\}}  \leq L_{\mathit{total}} < L_A + L_B\]

@@

Assume we generate $1024$ random inputs and record the memory access each time. For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution. After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}. Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent.  We calculate the expected value for the observation $ab$ based on the frequency.
\[ E_{ab} = \frac{(255+256)*(255+253)}{1024} = 255.5\]
Similarly, we calculate the rest expected values with the hypothesis that the leakages are independent and fill in them in Figure~\ref{chapter5:fig:con_table}. The degree of freedom $v$ is $(2-1)*(2-1) = 1$.

>>>>

\subsection{Channel Capacity}
$K$ is a random variable.
Let $k$ be one of the possible
values of $K$. The Shannon entropy $H(K)$ is defined as
\begin{equation}\label{chapter5:eq1}
  H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
\end{equation}

@@

\begin{mydef}
  \label{chapter5:def}
    Suppose we have a program $\beta$ with the input space $K$ and observation set $O$. We randomly select $k_1, k_2, \ldots, k_n \in K$ as the input and get observations $o_1, o_2, \ldots, o_n \in O$. Assume $K'=\{k_1, k_2, \ldots, k_n\}$  ($K' \subseteq K$) and
    $O'=\{o_1, o_2, \ldots, o_n\}$  ($O' \subseteq O$).
    We denote it as
    $$\beta(K') \rightarrow	O'.$$
    %Here $O$ is a set that consists of various observations $o_1, o_2, \dots, o_m$.
    The amount of leaked information $L_{\beta(K')\rightarrow O'}$ based on the observations ($O'$) is
    $$L_{\beta(K')\rightarrow O'} = H(O') = - \sum_{o {\in} O'}p(o)\log_2(p(o)). $$
\end{mydef}

@@

Suppose one program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution.
Depending on the relation between A and B, the total leaked information $L_{\mathit{AB}}$ will be:

\subsection{Independent Leakages}
If any observation of A does not affect the probability of occurrence of the any observation leakage B, we call the two leakage sites A and B are independent.
If A and B are two independent leakages, the total amount of leaked information is:
\[L_{\mathit{AB}} = - \sum_{k {\in} K}p(k)\log_2(p(k)) = L_A + L_B \]

\subsection{Dependent Leakages}
If A and B are dependent leakages, the total information leakage will be:
\[\max{\{L_A, L_B\}}  \leq L_{\mathit{AB}} < L_A + L_B\]

@@

Assume we generate $1024$ random inputs and record the memory access each time.  After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}. Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent.  We calculate the expected value for the observation $ab$ based on the frequency.
\[ E_{ab} = \frac{(255+256)*(255+253)}{1024} = 255.5\]
Similarly, we calculate the rest expected values with the hypothesis that the leakages are independent and fill in them in Figure~\ref{chapter5:fig:con_table}. The degree of freedom $v$ is $(2-1)*(2-1) = 1$.
